---
title: "Probabilistic Forecast Evaluation Report"
header-includes:
   - \usepackage{float}
   - \usepackage{color}
output: pdf_document
params:
    path_to_github: "../../../covid-19"
    path_to_data: "../../../state_level_upstream_df/upstream_df_state_2020-06-29_final.RData"
    scorecard_files: "path_to_scorecards_separated_by_semicolons"
always_allow_html: true
---
```{r setup, include = FALSE, echo = FALSE}
library(tidyverse)
library(lubridate)
library(knitr)
library(ggthemes)
library(latex2exp)
library(kableExtra)

knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, fig.width = 8)

getOutputFormat <- function() {
  output <- rmarkdown:::parse_yaml_front_matter(
    readLines(knitr::current_input())
    )$output
  if (is.list(output)){
    return(names(output)[1])
  } else {
    return(output[1])
  }
}
output_format = getOutputFormat()
```

[comment]: # #################################################################
[comment]: # #             BEGINNING OF DATA LOADING CODE BLOCKS             #
[comment]: # #################################################################

```{r global-settings}
# TODO: USER UPDATES THESE:
path_to_github <- params$path_to_github
forecast_repo <- params$forecast_repo
path_to_data <- params$path_to_data
```

```{r wrap-hook, include = FALSE}
hook_output = knit_hooks$get('output')
knit_hooks$set(output = function(x, options) {
  # this hook is used only when the linewidth option is not NULL
  if (!is.null(n <- options$linewidth)) {
    x = knitr:::split_lines(x)
    # any lines wider than n should be wrapped
    if (any(nchar(x) > n)) x = strwrap(x, width = n)
    x = paste(x, collapse = '\n')
  }
  hook_output(x, options)
})
```

This file takes in multiple score cards and an upstream data frame, and shows
the standard evaluation metrics and plots we like:
```{r load data, echo = FALSE, include = FALSE}
scorecard_files <- str_split(params$scorecard_files, ";")[[1]]
score_cards_list <- scorecard_files %>% map(readRDS)
forecaster_names <- score_cards_list %>%
  map_chr(~ attr(.x, "metadata")$name)
# this next bit is to address a bug that still needs to be fixed in which
# some forecasters are called "your_quantile_forecaster"
forecaster_names_from_file_structure <- scorecard_files %>% 
  str_split("/") %>%
  map_chr(~ .x[length(.x) - 1])
forecaster_names <- if_else(forecaster_names == "your_quantile_forecaster",
                            forecaster_names_from_file_structure,
                            forecaster_names)
names(score_cards_list) <- forecaster_names
load(path_to_data) # gives df
override <- TRUE

```

[comment]: # #################################################################
[comment]: # #                END OF DATA LOADING CODE BLOCKS                #
[comment]: # #         MODIFICATION OF SUBSEQUENT CODE BREAKS WARRANTY       #
[comment]: # #################################################################

```{r helper-mapping, echo=FALSE}
STATE_TO_FIPS = list("WA"="53", "DE"="10", "DC"="11", "WI"="55", "WV"="54",
"HI"="15", "FL"="12", "WY"="56", "PR"="72", "NJ"="34", "NM"="35", "TX"="48",
"LA"="22", "NC"="37", "ND"="38", "NE"="31", "TN"="47", "NY"="36", "PA"="42",
"AK"="02", "NV"="32", "NH"="33", "VA"="51", "CO"="08", "CA"="06", "AL"="01",
"AR"="05", "VT"="50", "IL"="17", "GA"="13", "IN"="18", "IA"="19", "MA"="25",
"AZ"="04", "ID"="16", "CT"="09", "ME"="23", "MD"="24", "OK"="40", "OH"="39",
"UT"="49", "MO"="29", "MN"="27", "MI"="26", "RI"="44", "KS"="20", "MT"="30",
"MS"="28", "SC"="45", "KY"="21", "OR"="41", "SD"="46")
```

```{r select locations, echo = FALSE}
locations_list = lapply(score_cards_list,function(u){unique(u$location)})
sc_locations = Reduce(intersect, locations_list)
common_locations = intersect(sc_locations, df$location)
num_locations = length(common_locations)

# Make sure that the df and scorecard only contain locations for which all forecasters
# knew they were predicting.
df <- df %>% filter(location %in% common_locations)
for(score_card in score_cards_list){
  score_card <- score_card %>% filter(location %in% common_locations)
}
```

```{r check data, echo = FALSE, linewidth = 60}
attributes_list <- lapply(score_cards_list, function(u){attr(u, "metadata")})
if(any(sapply(attributes_list, is.null))){
  cat(sprintf("Warning: Scorecards %s do not have metadata for attributes.  Please confirm the scorecards are for the same task.",
              paste(names(score_cards_list)[sapply(attributes_list, is.null)], collapse = ", ")), fill = TRUE)
}

response_list <- unlist(lapply(attributes_list, function(u){u$response}))
ahead_list <- unlist(lapply(attributes_list, function(u){u$ahead}))
incidence_period_list <- unlist(lapply(attributes_list, function(u){u$incidence_period}))
geo_type_list <- unlist(lapply(attributes_list, function(u){u$geo_type}))
err_measure_list <- unlist(lapply(attributes_list, function(u){u$err_measure}))
backfill_buffer_list <- unlist(lapply(attributes_list, function(u){u$backfill_buffer}))
n_locations_list <- unlist(lapply(attributes_list, function(u){u$n_locations}))

metadata_list <- list(response = response_list, 
                      ahead = ahead_list, 
                      incidence_period = incidence_period_list, 
                      geo_type = geo_type_list, 
                      err_measure = err_measure_list, 
                      backfill_buffer = backfill_buffer_list,
                      n_locations = n_locations_list)


if(length(response_list) > 0){
  check <- sapply(metadata_list, function(u){length(unique(u[!is.na(u) & !is.null(u)])) == 1})
  
  if(any(!check)) {
    if(!override) stop(sprintf("The input scorecards do not agree on the following metadata parameters: %s.  Please check the metadata using `attr(score_card, 'metadata')`.  You can override this check by setting override = TRUE in the header.",
                               paste(names(check)[!check], collapse = ", ")))
    else cat("Metadata check overridden", fill = TRUE)
  } 
  
  response <- response_list[1]
  cat(sprintf(" response : %s \n ahead : %s \n incidence_period : %s \n geo_type : %s \n err_measure : %s \n backfill_buffer : %s",response_list[1], ahead_list[1], incidence_period_list[1], geo_type_list[1], err_measure_list[1], backfill_buffer_list[1]), fill = TRUE)
} else{
  cat(sprintf("No metadata.  Using %s as response", response), fill = TRUE)
  response <- "usafacts_deaths_incidence_num"
}
if (!(response %in% df$variable_name)) {
  old_name <- "usafacts_deaths_incidence_num"
  new_name <- "usa-facts_deaths_incidence_num"
  if (response ==  old_name & new_name %in% df$variable_name) {
    df <- df %>%
      mutate(variable_name = if_else(variable_name == new_name,
                                     old_name, variable_name))
  }
  else
    stop("response from score cards not found in df.")
}
```

```{r set-geo-type, echo=FALSE}
geo_type = geo_type_list[1]
if (geo_type == 'county') {
  geo_type_plural = 'counties'
  n_display_regions = 50
} else if (geo_type == 'state') {
  geo_type_plural = 'states'
  n_display_regions = 30
} else {
  stop(sprintf("Unrecognized geo_type: %s", geo_type))
}
```


```{r load evaluator-files, echo=FALSE, include = FALSE}
source(file.path(path_to_github,
                 "hospitalization",
                 "pipeline",
                 "evaluation_pipeline",
                 "prob_forecast_evaluation_coverage.R"))
# for population size:
geo_info <- read_csv(file.path(path_to_github,
                             "demographics",
                             "data",
                             paste0(geo_type, "-health-rankings.csv")))
# TODO: UPDATE THIS
## The `location` column should be FIPS or two-letter postal (lowercase)
## The `location_name` column should either be upper postal or full state name
if (geo_type == 'county') {
  geo_info <- geo_info %>% transmute(
      location = fips,
      location_name = county,
      population = chr_population,
    )
} else if (geo_type == 'state') {
    # TODO: Conform column names to flexible to both state and county.
  geo_info <- geo_info %>% transmute(
      location = sapply(state,
                        function(x) STATE_TO_FIPS[[str_to_upper(x)]]),
      location_name = toupper(state),
      population = chr_population,
  )
} else {
  stop(sprintf("Unrecognized geo_type: %s", geo_type))
}
source(file.path(path_to_github,
                 "hospitalization",
                 "pipeline", 
                 "evaluation_pipeline", 
                 "diagnose.R"))
```

```{r setup kable, include = FALSE, echo = FALSE}

dates <- lapply(score_cards_list, function(u){unique(pull(u, forecast_date))})

common_dates <- as.Date(base::Reduce("intersect", dates), origin = "1970-01-01")
num_dates <- length(common_dates)

stopifnot((num_dates > 0) & (num_locations > 0))
score_cards_list <- lapply(score_cards_list,
                           function(u){filter(u, forecast_date %in% common_dates
                                              &  location %in% common_locations
                                              )})

stopifnot(is.data.frame(df))

if ("html_document" %in% rmarkdown::all_output_formats(knitr::current_input())){
  kable_format <- "html"
} else if("pdf_document" %in% rmarkdown::all_output_formats(knitr::current_input())){
  kable_format <- "latex"
} else{
  warning("Trying to knit to something other than pdf or html; kableExtra may not support it; contact Samyak")
  kable_format <- "html"
}
```

```{r initial calculations-1, include = FALSE}
## Gather the names of the scorecards
names_list <- data.frame(straw = 1:length(score_cards_list), scorecard = names(score_cards_list)) %>% 
  mutate(straw = as.numeric(as.character(straw)),
         scorecard = as.character(scorecard))

## Bind the score cards together
score_card_bound <- 
  bind_rows(score_cards_list, .id = "scorecard") %>% left_join(names_list, by = "scorecard") %>%
  mutate(err_abs = get_median_error(actual, forecast_distribution)) %>% 
  mutate(err_abs_log = get_median_log_error(actual, forecast_distribution))

nlist <- length(score_cards_list)

## This is for the tables
leftover_rows <- setdiff(1:(num_dates * nlist), c(nlist * (0:(num_dates-1)) + 1, nlist * (0:(num_dates-1)) + 2))

## This is for plots
colour_values <- c("black", "red", c("dodgerblue1","seagreen1", "plum1", "hotpink1"))
colour_values <- colour_values[1:nlist]

## This is top error locations (for table as well as diagnostic plots)
errs_by_location <- score_card_bound %>% 
  group_by(location, location_name, scorecard) %>% 
  summarize(mean_err_abs = mean(err_abs, na.rm = TRUE),
            mean_err = mean(err, na.rm = TRUE)) %>%
  ungroup()
```

```{r initial calculations-2, include = FALSE}


## 
if(nlist > 2) warning(sprintf("More than two scorecards.  Only showing differences between first two, %s - %s", names_list$scorecard[1], names_list$scorecard[2]))

err_names <- paste("err_abs", names_list$scorecard[1:2], sep = "_")

##
score_card_diff <- score_card_bound %>% 
  pivot_wider(id_cols = c(location, forecast_date, actual),
              names_from = scorecard,
              names_prefix = "err_abs_",
              values_from = err_abs) %>%
  mutate(err_abs_diff = !!rlang::sym(err_names[1]) - !!rlang::sym(err_names[2]))
```

```{r initial calculations-3, include = FALSE}

##
worst_errors_abs <- errs_by_location %>%
  group_by(scorecard) %>%
  top_n(n_display_regions, wt = mean_err_abs) %>% 
  arrange(desc(mean_err_abs)) %>%
  select(-mean_err)

worst_errors_scores <- errs_by_location %>%
  group_by(scorecard) %>%
  top_n(n_display_regions, wt = mean_err) %>% 
  arrange(desc(mean_err)) %>%
  select(-mean_err_abs)


worst_errors_regions <- worst_errors_abs %>%
  ungroup() %>%
  select(location) %>%
  distinct() %>%
  left_join(geo_info, by = "location") %>%
  top_n(n_display_regions)

biggest_regions <- geo_info %>%
  top_n(n_display_regions, wt = population)

diff_error_regions <- score_card_diff %>%
  left_join(geo_info, by = "location") %>%
  group_by(location, location_name) %>%
  summarise(mean_err_abs_diff = mean(abs(err_abs_diff))) %>%
  ungroup %>%
  top_n(n_display_regions, wt = mean_err_abs_diff)


predict_outbreak_regions <- score_card_bound %>%
  left_join(geo_info, by = "location") %>%
  group_by(scorecard, location, location_name.x) %>%
  mutate(max_actual = max(actual)) %>%
  filter(max_actual == 0 & err != 0) %>%
  ungroup() %>%
  group_by(scorecard) %>%
  top_n(4, wt = err_abs) %>%
  ungroup %>%
  select(location, location_name.x) %>%
  distinct() %>%
  head(n_display_regions)



locations_filter <- unique(c(worst_errors_regions$location,
                      biggest_regions$location, 
                      diff_error_regions$location, 
                      predict_outbreak_regions$location))

```

```{r initial calculations-4, include = FALSE}

##
min_plot_reference_date <- ymd(20200414)

diagnostic_plots <-
  diagnose_quantile_forecasters(
    df,
    score_cards = score_cards_list,
    locations = locations_filter,
    response = response,
    max_plots_per_page = 4,
    min_plot_reference_date = min_plot_reference_date
  )

pop_deciles <- geo_info %>% 
  pull(population) %>% 
  quantile(probs = seq(0, 1, length=11))
pop_deciles[1] <- pop_deciles[1] * 0.9
pop_deciles[11] <- pop_deciles[11] * 1.1
```


# Confidence intervals and coverage

### Coverage proportion (across locations):

In what fraction of locations is the actual value in $(\hat q_{\alpha/2},\hat q_{1-\alpha/2})$?  Does it match the nominal coverage of $1-\alpha$?

- We would like the coverage line to be at or above the line $y = x$.

```{r coverage line, echo=FALSE}
coverage_list <- lapply(score_cards_list, compute_coverage)

coverage_bound <- bind_rows(coverage_list, .id = "scorecard")

coverage_bound %>%
  pivot_longer(contains("prop"),
               names_to = "coverage_type",
               values_to = "proportion") %>% 
  filter(coverage_type == "prop_covered") %>%
  ggplot(aes(x = nominal_coverage_prob, 
             y = proportion,
             colour = scorecard
             )) +
  geom_line() + 
  # geom_col() +
  facet_wrap(~ forecast_date) +
  geom_abline(intercept = 0, slope = 1) + 
  labs(x = TeX("Nominal coverage, $(1 - \\alpha)$"),
       y = "Proportion",
       title = "Coverage") +
  geom_vline(xintercept = 0.6, lty = 2) + 
  xlim(0, 1) +
  ylim(0, 1) + 
  theme_bw() +
  scale_colour_manual(name = "",
                      values = colour_values,
                      breaks = names_list$scorecard) +
  NULL

```

\newpage

In what fraction of locations is the true value (strictly) above or below the nominal quantiles?

```{r wedge plot, echo = FALSE}
coverage_quantiles_list <- lapply(score_cards_list, compute_quantile_coverage)

wedgeplot_coverage <- function(coverage_quantiles, name){
coverage_quantiles %>%
  pivot_longer(contains("prop"),
               names_to = "coverage_type",
               values_to = "proportion") %>% 
  filter(coverage_type != "prop_covered") %>%
  mutate(alpha = ifelse((coverage_type == "prop_above" & nominal_quantile < 0.5) | 
                          (coverage_type == "prop_below" & nominal_quantile > 0.5), 0.5, 1)) %>% 
  ggplot(aes(x = nominal_quantile, 
             y = proportion,
             colour = coverage_type)) +
  geom_line(aes(alpha = alpha, size = alpha)) + 
  geom_point(aes(alpha = alpha, size = alpha)) +
  # geom_col() +
  facet_wrap(~ forecast_date) +
  geom_abline(intercept = 0, slope = 1) + 
  geom_abline(intercept = 1, slope = -1) + 
  labs(x = TeX("Nominal quantile"),
       y = "Proportion",
       title = sprintf("Quantile plots - %s", name)) +
  geom_vline(xintercept = c(0.2, 0.8), lty = 2) + 
  xlim(0, 1) +
  ylim(0, 1) + 
  theme_bw() +
  scale_colour_discrete(name = "") +
  scale_alpha_continuous(range = c(0.5, 1)) +
  scale_size_continuous(range = c(0.5, 1)) +
  guides(alpha = FALSE, size = FALSE) +
  NULL
}

for(i in 1:length(coverage_quantiles_list)){
  print(wedgeplot_coverage(coverage_quantiles_list[[i]], names_list$scorecard[i]))
}



```


\newpage

```{r}
first_forecast_date <- score_cards_list %>% 
  map(~ min(.x$forecast_date)) %>%
  unlist() %>% 
  min() %>% 
  as.Date(origin="1970-01-01")
thresh <- 5
above <- df %>% 
  filter(variable_name == response) %>% 
  filter(reference_date >= first_forecast_date - 7,
         reference_date <= first_forecast_date) %>% 
  select(-issue_date) %>%
  group_by(location) %>%
  summarize(tot = sum(value)) %>% 
    filter(tot >= thresh) %>% 
    pull(location)
num_above <- length(above)
```

There are `r num_above` `r geo_type_plural` with at least `r thresh` deaths in
the week leading up to `r first_forecast_date`.  Here are the same plots
restricted to just those `r geo_type_plural`.

```{r coverage line conditional, echo=FALSE}
conditional_coverage_list <- map(score_cards_list,
                                 function(u) {
                                   u <- u %>% filter(location %in% above)
                                   compute_coverage(u)
                                 })

conditional_coverage_bound <- bind_rows(conditional_coverage_list, .id = "scorecard")

conditional_coverage_bound %>%
  pivot_longer(contains("prop"),
               names_to = "coverage_type",
               values_to = "proportion") %>% 
  filter(coverage_type == "prop_covered") %>%
  ggplot(aes(x = nominal_coverage_prob, 
             y = proportion,
             colour = scorecard
             )) +
  geom_line() + 
  # geom_col() +
  facet_wrap(~ forecast_date) +
  geom_abline(intercept = 0, slope = 1) + 
  labs(x = TeX("Nominal coverage, $(1 - \\alpha)$"),
       y = "Proportion",
       title = "Coverage") +
  geom_vline(xintercept = 0.6, lty = 2) + 
  xlim(0, 1) +
  ylim(0, 1) + 
  theme_bw() +
  scale_colour_manual(name = "",
                      values = colour_values,
                      breaks = names_list$scorecard) +
  NULL

```

\newpage

```{r wedge plot conditional, echo = FALSE}
conditional_coverage_quantiles_list <- map(score_cards_list,
                                 function(u) {
                                   u <- u %>% filter(location %in% above)
                                   compute_quantile_coverage(u)
                                 })

for(i in 1:length(conditional_coverage_quantiles_list)){
  print(wedgeplot_coverage(conditional_coverage_quantiles_list[[i]], names_list$scorecard[i]))
}

```

\newpage

We now look at coverage within each decile.  In the following plot, we have overlaid the coverage lines at each decile.

```{r decile-coverage, echo = FALSE, fig.height=10}
deciles_coverage_plot <- function(score_card){
  score_card %>% left_join(
    geo_info %>% mutate(
        population_group = as.factor(cut(population,
                                         breaks = pop_deciles,
                                         labels = FALSE))
    ) %>% select(
      location,
      population_group,
    ), by = "location"
  ) %>% split(
    .$population_group
  ) %>% map_if(
    ~ nrow(.) > 0, compute_coverage
  ) %>% {.}
}

deciles_coverage_plot_lists <- lapply(score_cards_list, deciles_coverage_plot) %>%
  unlist(recursive = FALSE) %>%
  bind_rows(.id = "id") %>%
  separate(id, c("scorecard", "decile"), sep = "\\.") %>%
  mutate(decile = as.numeric(decile))


deciles_coverage_plot_lists %>%
  pivot_longer(contains("prop"),
               names_to = "coverage_type",
               values_to = "proportion") %>% 
  filter(coverage_type == "prop_covered") %>%
  ggplot(aes(x = nominal_coverage_prob, 
             y = proportion,
             colour = scorecard,
             group = decile
             )) +
  geom_line(aes(alpha = decile)) + 
  # geom_col() +
  facet_wrap(~ forecast_date + scorecard) +
  geom_abline(intercept = 0, slope = 1) + 
  labs(x = TeX("Nominal coverage, $(1 - \\alpha)$"),
       y = "Proportion",
       title = sprintf("Coverage at deciles")) +
  geom_vline(xintercept = 0.6, lty = 2) + 
  xlim(0, 1) +
  ylim(0, 1) + 
  theme_bw() +
  scale_colour_manual(name = "",
                      values = colour_values,
                      breaks = names_list$scorecard) +
  scale_alpha_continuous(breaks = 1:10) + 
  # guides(alpha = FALSE) +
  theme(legend.position = "bottom") +
  NULL

```

\newpage

## Median interval width (across locations)

What is the median length (across locations) of $(\hat q_{\alpha/2},\hat q_{1-\alpha/2})$? How does it differ by day?

```{r interval-width, echo = FALSE,warning = FALSE, fig.width = 9, fig.height = 11}
diagnostic_plots$interval_width_boxplot

diagnostic_plots$interval_width_plot + 
  geom_vline(xintercept = 0.6, lty = 2)
```

# Boxplots

### Boxplot of Absolute errors:

```{r boxplot-err_abs, echo = FALSE}
score_card_bound %>% 
  ggplot(aes(x = as.factor(forecast_date), y = log(1+err_abs), colour = scorecard)) +
  geom_boxplot() + 
  # scale_y_log10() + 
  labs(x = "Forecast Date",
       y = "log_pad(Absolute error)",
       title = sprintf("Forecaster performance over time (all %s)", geo_type_plural)) +
  scale_colour_manual(values = colour_values,
                      breaks = names_list$scorecard) + 
  theme_bw()
```

```{r boxplot-err_abs_b, echo = FALSE}
score_card_bound %>% 
  filter(location %in% above) %>% 
  ggplot(aes(x = as.factor(forecast_date), y = log(1+err_abs), colour = scorecard)) +
  geom_boxplot() + 
  # scale_y_log10() + 
  labs(x = "Forecast Date",
       y = "log_pad(Absolute error)",
       title = sprintf("Forecaster performance over time (%s w/ >= %s deaths in week before %s)",
                       geo_type_plural,
                       thresh,
                       first_forecast_date)) +
  scale_colour_manual(values = colour_values,
                      breaks = names_list$scorecard) + 
  theme_bw()
```

\newpage
Number of locations where the scorecards have the same error, and number of locations where we cannot compare due to NAs predictions:

```{r na_howmany, echo = FALSE}
score_card_diff %>%
  group_by(forecast_date) %>%
  summarise(`Zero Pred & Error` = sum(err_abs_diff == 0 & actual == 0, na.rm = TRUE),
            `NA Error` = sum(is.na(err_abs_diff))) %>%
  kable(format = kable_format)
```


  

## Boxplot of differences in Absolute Errors, when the two scorecards have different errors:

```{r boxplot-err_abs_diff, echo = FALSE}
score_card_diff %>%
  filter(!(err_abs_diff == 0 & actual == 0), !is.na(err_abs_diff)) %>%
  ggplot(aes(x = as.factor(forecast_date), y = sign(err_abs_diff)*log(1+abs(err_abs_diff)))) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_boxplot() +
  labs(x = "Forecast Date",
       y = "signed_log_pad(difference of err_abs)",
       title = sprintf("Boxplot of Difference in absolute error \n%s - %s", err_names[1], err_names[2])) +
  theme_bw()
```

Same idea but restricted to the `r num_above` `r geo_type_plural` having at
least `r thresh` deaths in the week leading up to `r first_forecast_date`:

```{r boxplot-err_abs_diff_b, echo = FALSE}
score_card_diff %>%
  filter(location %in% above) %>% 
  filter(!(err_abs_diff == 0 & actual == 0), !is.na(err_abs_diff)) %>%
  ggplot(aes(x = as.factor(forecast_date), y = sign(err_abs_diff)*log(1+abs(err_abs_diff)))) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_boxplot() +
  labs(x = "Forecast Date",
       y = "signed_log_pad(difference of err_abs)",
       title = sprintf("Boxplot of Difference in absolute error \n%s - %s", err_names[1], err_names[2])) +
  theme_bw()
```

\newpage

## Scatterplot of Absolute Errors:

```{r scatterplot, echo = FALSE}

score_card_diff %>%
  filter(!(err_abs_diff == 0 & actual == 0), !is.na(err_abs_diff)) %>%
  left_join(geo_info, by = "location") %>%
  group_by(forecast_date) %>%
  top_n(300, wt = population) %>%
  ungroup() %>%
  mutate(population_group = (cut(population,
                                 breaks = quantile(population, 
                                                    probs = seq(0, 1, by = 0.1)) * 
                                   c(0.9, rep(1, 9), 1.1),
                                 labels = FALSE))) %>%
  ggplot(aes(x = log(1 + !!rlang::sym(err_names[1])), y = log(1 + !!rlang::sym(err_names[2])))) +
  facet_wrap(~ forecast_date) +
  geom_point(aes(size = population_group), alpha = 0.15, colour = "darkgreen") +
  geom_abline(intercept = 0, slope = 1) +
  guides(size = FALSE,
         alpha = FALSE) +
  coord_fixed() +
  theme_bw() + 
  labs(x = names_list$scorecard[1], 
       y = names_list$scorecard[2],
       title = sprintf("Absolute Errors on log scale, top 300 %s by population",
                       geo_type_plural)) +
  NULL

```


### Which locations have `NA` for their error?

```{r na_loc, echo = FALSE}
na_tbl <- score_card_bound %>% 
  filter(na_prediction) %>% 
  group_by(scorecard) %>%
  count(location) %>%
  ungroup
if (nrow(na_tbl) > 0) {
  na_tbl %>%
  rename(num_dates_missing = n) %>% 
  kable(format = kable_format)
} else {
  cat("No NAs!", fill = TRUE)
}
```

\newpage
# Tables

### Absolute error: (`abs(actual - median)`)

Across all `r geo_type_plural`:

```{r table1, echo = FALSE}
table_quantiles = c(.5, .70, .80, .90, .95, 0.99)
score_card_bound %>%
  group_by(forecast_date, scorecard, straw) %>% 
  group_modify(~ enframe(my_summary(.x$err_abs, quantiles = table_quantiles))) %>% 
  pivot_wider(names_from = name, values_from = value) %>% 
  ungroup() %>%
  arrange(forecast_date, straw) %>%
  select(-straw) %>%
  kable(format = kable_format, digits = 2) %>%
  kable_styling() %>% 
  row_spec(row = nlist * (0:(num_dates-1)) + 1, bold = TRUE) %>%
  row_spec(row = nlist * (0:(num_dates-1)) + 2, italic = TRUE, color = "red") %>%
  row_spec(row = leftover_rows, italic = TRUE)
```

Across the `r num_above` having at least `r thresh` deaths in the week leading up to `r first_forecast_date`:

```{r table1b, echo = FALSE}
score_card_bound %>%
  filter(location %in% above) %>% 
  group_by(forecast_date, scorecard, straw) %>% 
  group_modify(~ enframe(my_summary(.x$err_abs, quantiles = table_quantiles))) %>% 
  pivot_wider(names_from = name, values_from = value) %>% 
  ungroup() %>%
  arrange(forecast_date, straw) %>%
  select(-straw) %>%
  kable(format = kable_format, digits = 2) %>%
  kable_styling() %>% 
  row_spec(row = nlist * (0:(num_dates-1)) + 1, bold = TRUE) %>%
  row_spec(row = nlist * (0:(num_dates-1)) + 2, italic = TRUE, color = "red") %>%
  row_spec(row = leftover_rows, italic = TRUE)
```

### Absolute error on log scale: (`abs(log_pad(actual) - log_pad(median))`)
```{r table2, echo = FALSE}
score_card_bound %>%
  group_by(forecast_date, scorecard, straw) %>% 
  group_modify(~ enframe(my_summary(.x$err_abs_log, quantiles = table_quantiles))) %>% 
  pivot_wider(names_from = name, values_from = value) %>% 
  ungroup() %>%
  arrange(forecast_date, straw) %>%
  select(-straw) %>%
  kable(format = kable_format, digits = 2) %>%
  kable_styling() %>% 
  row_spec(row = nlist * (0:(num_dates-1)) + 1, bold = TRUE) %>%
  row_spec(row = nlist * (0:(num_dates-1)) + 2, italic = TRUE, color = "red") %>%
  row_spec(row = leftover_rows, italic = TRUE)
```

### Weighted interval score:
```{r table3, echo = FALSE}
score_card_bound %>%
  group_by(forecast_date, scorecard, straw) %>% 
  group_modify(~ enframe(my_summary(.x$err, quantiles = table_quantiles))) %>% 
  pivot_wider(names_from = name, values_from = value) %>% 
  ungroup() %>%
  arrange(forecast_date, straw) %>%
  select(-straw) %>%
  kable(format = kable_format, digits = 2) %>%
  kable_styling() %>% 
  row_spec(row = nlist * (0:(num_dates-1)) + 1, bold = TRUE) %>%
  row_spec(row = nlist * (0:(num_dates-1)) + 2, italic = TRUE, color = "red") %>%
  row_spec(row = leftover_rows, italic = TRUE)
```












\newpage
## Errors by location:


### By population size:


```{r deciles-boxplots, echo = FALSE, fig.height = 8}

score_card_bound %>% 
  filter(!is.na(err)) %>% 
  left_join(geo_info %>%
              mutate(population_group = as.factor(cut(population,
                                                      breaks = pop_deciles,
                                                      labels = FALSE))) %>%
              select(location, population_group),
            by = "location") %>% 
  ggplot(aes(x = population_group, y = log(1+err), colour = scorecard)) +
  geom_boxplot() +
  # scale_y_log10() +
  facet_wrap(~ forecast_date, ncol = 2) +
  labs(x = "Population Decile",
       y = "log_pad(err)") +
  theme(legend.position = "bottom") +
  scale_colour_manual(name = "",
                      values = colour_values,
                      breaks = names_list$scorecard) +
  theme_bw() +
  theme(legend.position = "bottom") +
  NULL
```

The population sizes defining the deciles are as follows:
```{r, echo=FALSE}
pop_deciles[c(-1, -11)]
```

\newpage

**`r str_to_title(geo_type_plural)` by average point estimate error:**
```{r, echo = FALSE}
# Locations sorted by mean absolute error across all scorecards
location_by_error <- errs_by_location %>%
  group_by(location) %>%
  summarise(global_mean_err_abs = mean(mean_err_abs,na.rm = T)) %>%
  ungroup() %>%
  arrange(desc(global_mean_err_abs)) %>%
  top_n(n_display_regions, wt = global_mean_err_abs)

# Errors by location table
errs_by_location_all_scorecards <- errs_by_location %>%
  select(-mean_err) %>%
  pivot_wider(names_from = "scorecard",values_from = "mean_err_abs") %>%
  right_join(location_by_error,by = "location")

round1 <- function(x){round(x,1)}
errs_by_location_tbl <- errs_by_location_all_scorecards %>%
  mutate_if(is.numeric,list(round1)) %>%
  mutate_all(as.character)
for(ii in 1:nrow(errs_by_location_tbl))
{
  competitors <- errs_by_location_tbl[ii,] %>% 
    select(-c(location,location_name,global_mean_err_abs)) %>%
    names()
  winner <- errs_by_location_tbl[ii,competitors] %>% 
    mutate_all(as.numeric) %>%
    which.min() %>% 
    names()
  loser <- errs_by_location_tbl[ii,competitors] %>% 
    mutate_all(as.numeric) %>%
    which.max() %>% 
    names()
  
  # color the winner green, and the loser red
  if  (output_format == 'pdf_document') {
    errs_by_location_tbl[ii,winner] <- paste0("\\textcolor{green}{",errs_by_location_tbl[ii,winner],"}")
    errs_by_location_tbl[ii,loser]  <- paste0("\\textcolor{red}{",errs_by_location_tbl[ii,loser],"}")
  } else if (output_format == 'html_document') {
    errs_by_location_tbl[ii,winner] <- paste0("<span style = \"color:green\">",
                                              errs_by_location_tbl[ii,winner],
                                              "</span>")
    errs_by_location_tbl[ii,loser]  <- paste0("<span style = \"color:red\">",
                                              errs_by_location_tbl[ii,loser],
                                              "</span>")
  }
}

# Give the locations a more parsimonious name
errs_by_location_tbl[["location_name"]] <- gsub("County","",errs_by_location_tbl[["location_name"]])
errs_by_location_tbl %>%
  select(-c(location,global_mean_err_abs)) %>%
  kable(format = "markdown")
```

```{r echo = FALSE, linewidth = 60}
sprintf("The %d %s with the worst absolute errors across all scorecards are: %s",
          n_display_regions,
          geo_type_plural,
          paste(worst_errors_regions$location_name, collapse = ", "))

sprintf("The top %d biggest %s are: %s", 
          n_display_regions,
          geo_type_plural,
          paste(biggest_regions$location_name, collapse = ", "))

sprintf("The top %d %s with the largest difference in error between the scorecards are: %s",
          n_display_regions,
          geo_type_plural,
          paste(diff_error_regions$location_name, collapse = ", "))

sprintf("The top %d %s with zero actual counts but nonzero predictions are: %s",
          n_display_regions,
          geo_type_plural,
          paste(predict_outbreak_regions$location_name, collapse = ", "))
```


\newpage
# Time Series Plots

**Plots of predicted vs. actual for the locations selected:**

```{r time-series-plots,echo = FALSE,warning = FALSE, fig.height=11, fig.width = 9}
time_series_plots <- diagnostic_plots$time_series_plots
for(i in 1:length(time_series_plots)){
  print(time_series_plots[[i]])
  cat("\n")
}

```

\newpage
**Plots of residuals for the locations selected:**

```{r residuals-plots,echo = FALSE,warning = FALSE, fig.height=11, fig.width = 9}
residual_plots <- diagnostic_plots$residual_plots
for(i in 1:length(residual_plots)){
  print(residual_plots[[i]])
  cat("\n")
}
```

